### 2022-01-20 src-latex/main-paper.tex
review of section 4
Shrink acknowledgments

\documentclass[runningheads,svgnames]{llncs}
%
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cleveref}
% \usepackage{tikz}
% \usepackage{nth}
% \usepackage{subcaption}
\usepackage{booktabs}
% \usepackage{array}
\usepackage{orcidlink}
\usepackage{subcaption} % Addition
\usepackage{multirow} % Addition
\usepackage{tabularx} % Addition
\usepackage{booktabs} % Addition
\usepackage{scalerel}
\usepackage{cleveref}

@@

\section*{Acknowledgments}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.

The authors want to thank Stéphane Bacciochi and Pascal Cristofoli for helping to create the gold reference dataset, 
Laureencia Maurice for annotating data,
as well as Guillaume Thomas, Paul Abi Saad, Raphaël Lelièvre, Dorian Mignon, Thibault Cavaciuti and Pierre Sadki for contributing to the annotation platform.
\joseph{On peut essayer de gagner de la place en déplaçant ça en footnote de 1ere page.}

>>>>

\documentclass[runningheads,svgnames]{llncs}
%
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cleveref}
% \usepackage{tikz}
% \usepackage{nth}
% \usepackage{subcaption}
\usepackage{booktabs}
% \usepackage{array}
\usepackage{orcidlink}
\usepackage{subcaption} % Addition
\usepackage{multirow} % Addition
\usepackage{tabularx} % Addition
\usepackage{booktabs} % Addition
\usepackage{siunitx} % Addition
\usepackage{scalerel}
\usepackage{cleveref}

@@

\section*{Acknowledgments}
This work is supported by the French National Research Agency (ANR), as part of the SODUCO project, under Grant ANR-18-CE38-0013.
%
The authors want to thank S. Bacciochi and P. Cristofoli for helping to create the reference dataset, 
L. Morice for annotating data,
as well as G. Thomas, P. Abi Saad, R. Lelièvre, D. Mignon, T. Cavaciuti and P. Sadki for contributing to the annotation platform.
%
% Full names
% Stéphane Bacciochi
% Pascal Cristofoli
% Laureencia Morice
% Guillaume Thomas
% Paul Abi Saad
% Raphaël Lelièvre
% Dorian Mignon
% Thibault Cavaciuti
% Pierre Sadki
